---
title: 
author: 
date: "9/16/2021"
output: pdf_document
---
##Introdutcion

In this homework we were challenged to test how does the maternal smoking affect birthweight.

We divided the work in some steps that we will describe in the next segments. Those steps are:
1.	Data gathering and construction
2.	Descriptive Statistics and other analysis
3.	Multilinear regression analysis
4.	How to perfect our regression
5.	Go beyond the problem

##1. Data gathering and construction

``{r}

install.packages( "rmarkdown" )
install.packages( "data . table " )
install.packages( "ggplot2 " )
install.packages( " stargazer " )
install.packages( "lmtest " )
install.packages( "sandwich" )
install.packages( "mfx" )
install.packages( "ggthemes" )
install.packages( "Metrics " )
install.packages( "GGally" )
install.packages( "mgcv" )
install.packages( "munsell" )
install.packages( "plm" )
install.packages( "Formula" )
install.packages( "ggthemes" )
install.packages( "cowplot" )
install.packages( "corrgram" )

``


Packages to install:
```{r message=FALSE, warning=FALSE}
#install.packages('ggplot2')
#install.packages('Hmisc')
#install.packages('datasets')
#install.packages('stargazer')
#install.packages('data.table')
#install.packages('reshape2')
#install.packages('lmtest')
#install.packages('zoo')
```

Activate the packages:
```{r message=FALSE, warning=FALSE}
#library(ggplot2)
#library(Hmisc)
#library(datasets)
#library(stargazer)
#library(data.table)
#library(reshape2)
#library(lmtest)
#library(zoo)
```

Load the data:

```{r}
library(readr)
data <- read_csv("data.csv")

```


Transforming the data in data table:


```{r}
library(data.table)
path_to_data <- "data.csv" 
#View(fread(path_to_data, nrows = c(100)))

desired_vars <- c("dob_mm", "mager", "mbrace", "fbrace", "previs", "cig_0", "cig_1", "cig_2", "cig_3", "m_ht_in", "bmi", "sex", "combgest", "dbwt", "meduc", "feduc", "rf_pdiab", "rf_gdiab", "rf_phype", "rf_ghype", "ilop_r", "ld_ster", "rf_ehype", "restatus")

data1 <- fread(path_to_data, select = desired_vars)

```          
  
  
  
We delete all the months except the June, that is what we want to study   
```{r}
rm(data)
data <- data1
rm(data1)

# Month June
data <- data[which(data$dob_mm==6),]  

#View(data)

```  

We take off all the data messing 

```{r}
#Taking out the missing information 

data <- data[which(data$mbrace== list( 1 , 2)),] # mother race
data <- data[which(data$restatus !=4),] # Residence Status 
data <- data[which(data$fbrace !=9),]  #father race
data <- data[which(data$previs !=99),] #Number of Prenatal Visits
data <- data[which(data$cig_0 !=99),] #Cigarettes
data <- data[which(data$cig_1 !=99),] #Cigarettes
data <- data[which(data$cig_2 !=99),] #Cigarettes 
data <- data[which(data$cig_3 !=99),] #Cigarettes 
data <- data[which(data$m_ht_in !=99),] #Mother’s Height in Total Inches	 
data <- data[which(data$bmi !=99.9),] #Body Mass Index 
data <- data[which(data$combgest !=99),] #Combined Gestation – Detail in Weeks	 
data <- data[which(data$dbwt !=9999),] #Consider non missing information in variable dbwt Birth Weight – Detail in Grams
data <- data[which(data$meduc !=9),] #Mother’s Education
data <- data[which(data$feduc !=9),] #163 1 FEDUC Father’s Education  
data <- data[which(data$rf_pdiab !="U"),] #Pre-pregnancy Diabetes
data <- data[which(data$rf_gdiab !="U"),] #Gestational Diabetes	 
data <- data[which(data$rf_phype !="U"),] #Pre-pregnancy Hypertension 
data <- data[which(data$rf_ghype !="U"),] #Gestational Hypertension
data <- data[which(data$ilop_r  !="999"),] #Interval Since Last Other Pregnancy Recode 
data <- data[which(data$ld_ster !="U"),] #Steroids	 
data <- data[which(data$rf_ehype !="U"),] #Hypertension Eclampsia

#data <- data.table(data)

summary(data)
```    

1st Part
Look to the Cigarettes influence 

````{r}
stargazer(data[, list(dbwt,cig_0, cig_1, cig_2, cig_3)], type ="text")   

````
   
 
````{r}
cor( data[ , list(dbwt, cig_0, cig_1, cig_2, cig_3)], y=NULL, use = "complete")

```  
   
   
   
   
   
   
   
2cd Part 

We look for more variables that can influence the birthweight
   
```{r}

stargazer(data[ , list(dbwt, mager, mbrace, fagecomb, fbrace, previs, cig_0, cig_1, cig_2, cig_3, m_ht_in, bmi, combgest, meduc, feduc, ilop_r)], type ="text")
```

           
           
           
           
        
           
           
           
```{r}


cor( data[ , list(dbwt, mager, mbrace, fagecomb, fbrace, previs, cig_0, cig_1, cig_2, cig_3, m_ht_in, bmi, combgest, meduc, feduc, ilop_r)], y=NULL, use = "complete")


```


lest create a new data tabel with just the date that are necessary. 

```{r}

```





View the data before the treatment:
```{r}
install.packages( "rmarkdown" )
install.packages( "data . table " )
install.packages( "ggplot2 " )
install.packages( " stargazer " )
install.packages( "lmtest " )
install.packages( "sandwich" )
install.packages( "mfx" )
install.packages( "ggthemes" )
install.packages( "Metrics " )
install.packages( "GGally" )
install.packages( "mgcv" )
install.packages( "munsell" )
install.packages( "plm" )
install.packages( "Formula" )
install.packages( "ggthemes" )
install.packages( "cowplot" )
install.packages( "corrgram" )

```




```{r}

````





##Analise the varible of smokeres parents



##Other variables that can have a big effect on the weigh of the babies

The wealth of the families 
The region of the parents
The weigh of the parents
The genre of the babes

Ter em atenção os N.A. values pk são importantes
diferença entre mean e medium 


##Conclusion



